Landscape composition and beneficial insects

### 2020-06-24 manuscript/manuscript_outline.Rmd
Worked on discussion. Added refs

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
 + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
 + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
 + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
 + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may

>>>>

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
 + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
 + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
 + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
 + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may be inappropriate feeding or nesting cover for _P. melanarius_.
 + To our knowledge, there is no published research demonstrating this
